Sparse Word Embedding for Multi-domain Machine Translation

### 2019-04-09 2019/emnlp/sparse.tex
new

To evaluate the performance of proposed architecture, we use 4 corpora for training: European Medicines Agency; European Central Bank, News-commentary and European Parliament \cite{Tiedemann2009RANLP5} corresponding to 4 domains: medical, banking, news and administrative  respectively and one non-domain corpora Common-crawl  which was introduced in Shared Task: Machine Translation of News the Third Conference On Machine Translation 2018(WMT2018). We use Khresmoi-dev, a test set used in the Biomedical Translation Task (WMT2018), newstest2008, and test2006 as validation set for domains: medical, news administrative; except for banking domain, we use a subset of size 2000 extracted from original corpora and excluded from training set. To test the model, we use Khresmoi-test; newstest2009 and test2007 for domains: medical, news administrative; except for banking domain, we use a subset of size 2000 extracted from original corpora and excluded from training set. The information of used corpora is presented in table \ref{table:Corpora}

\begin{table}[H]
\resizebox{\columnwidth}{!}{
\begin{tabular}{ |l|l|l|l|l|l| }
\hline
Task & Corpora & Train & Dev & Test & Vocabulary \\ \hline
\multirow{5}{*}{$English \rightarrow French$} & European Medicines Agency & 1092568 & 500 & 1000 & \\
 & European Central Bank & 191960 & 2000 & 2000 &\\
 & News-commentary & 258432 & 2051 & 3027 & \\
 & European Parliament & 2007723 & 2000 & 2000 & \\
 & Common-crawl & 3244152 &  &  & \\ \hline
\multirow{5}{*}{$English \rightarrow German$} & European Medicines Agency & 1108752 & 500 & 1000 & \\
 & European Central Bank & 109174 & 2000 & 2000 &\\
 & News-commentary & 270769 & 2051 & 2525 & \\
 & European Parliament & 1920209 & 2000 & 2000 & \\ 
 & Common-crawl & 2399123 &  &  & \\ \hline
\hline
\end{tabular}
}
\caption{Corpora}
\label{table:Corpora}
\end{table}

\subsection{NMT engine}

\subsection{Results}
\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 25.7 \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score in language pair English - French. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse(2) uses generic tag for all of test sets. Sparse(3) uses tag predicted by pretrained domain classififer}
\label{tab:1}
\end{figure}

\begin{figure}[H]
\caption{BLEU score in language pair English - German}
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\label{tab:2}
\end{figure}
\section{Conclusions}

>>>>

To evaluate the performance of proposed architecture, we design experiments in which we want to train an NMT for 3 domains such as medical, administrative documents and business briefly denoted by EMEA, EPPS, ECB according to training corpora name respectively. We use 3 corpora for training: European Medicines Agency; European Central Bank and European Parliament \cite{Tiedemann2009RANLP5}. We randomly split those 3 corpora into training, validation and test set with size described in table \ref{table:Corpora}. We use validation sets for choosing the best model according to the average BLEU score on 3 validation sets. We also realize that the test sets origined from same corpora as training sets are likely easy for trained model, thus can not provide fair evaluation. Therefore, we we use Khresmoi-test; newstest2009 and test2007 for domains: EMEA, EPPS. Unfortunately, we could not find any official test sets for ECB domain. We also want to evaluate the generalization of trained model. The model is also required to achieve comparable performance to generic model. To do so, we use newstest 2009 and IWSLT 2010 whose contain does not particularly belong to any domain.

\begin{table}[H]
\resizebox{\columnwidth}{!}{
\begin{tabular}{ |l|l|l|l|l|l| }
\hline
Task & Corpora & Train & Dev & Test & Vocabulary \\ \hline
\multirow{5}{*}{$English \rightarrow French$} & European Medicines Agency & 1090568 & 1000 & 1000 & English: 30164, French: 30398\\
 & European Central Bank & 191960 & 1000 & 1000 &\\
 & European Parliament & 2005723 & 1000 & 1000 & \\ \hline
\multirow{5}{*}{$English \rightarrow German$} & European Medicines Agency & 1108752 & 1000 & 1000 & English: 30159, German: 30698\\
 & European Central Bank & 111174 & 1000 & 1000 &\\
 & European Parliament & 1920209 & 1000 & 1000 & \\ \hline
\hline
\end{tabular}
}
\caption{Corpora}
\label{table:Corpora}
\end{table}
\subsection{NMT model configuration}
We evaluate our method on 2 popular architecture: Transformer of and Attentional Birectional Long Short-Term Memmory (LSTM).\\
More precisely, for Transformer we use the same setting as described in \cite{NIPS2017_7181}.For Attentional Birectional Long Short-Term Memmory, in order to fairly compare to the work of \cite{D18-1041}, we use standard configuration with: 1 layer bidirectional LSTM with hidden size 1024 in encoder; 1 layer attentional unidirectional LSTM with same hidden size in decoder; and word embedding of size 512. The code use Tensorflow and OpenNMT \cite{P17-4012}.\\
For sparse embedding implementation, we split vector embedding of size 512 into 4 regions $[8,8,8,488]$ corresponding to EMEA, EPPS, ECB domain and generic region. If sentence comes from domain $i$, Domain regions $j,\forall j \neq i$ will be masked as 0. We then use a dense layer of size 512 to fuse active domain region and generic region.
\subsection{Results}
\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.10 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 & 11.1 \\
 \hline
 ECB-finetuned & 9.2 & 18.39 & 55.45 & 12.13 & 16.12 & 8.71 & 7.19 \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score in language pair English - French. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse(2) uses generic tag for all of test sets. Sparse(3) uses tag predicted by pretrained domain classififer}
\label{tab:1}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. The notation is same as \ref{tab:1}}
\label{tab:2}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.10 \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as \ref{tab:1} except that other models from WDCMT of \cite{D18-1041} use Bidirectional-LTSM}
\label{tab:3}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline 
\end{tabularx}}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as \ref{tab:3}}
\label{tab:4}
\end{figure}

\section{Conclusions}
